Autonomous driving has for long been a relevant and important field of study. With the emergence of deep learning techniques and innovations regarding computing power and technology in vehicles, the field has only grown more prevalent.

The problem of different vehicles driving on the road together and while obeying the same set of rules can be modeled as an agent-based simulation, where each vehicle has its own set of goals but has to obtain information from the environment and act in accordance to it, 
even considering how other agents (vehicles) act within the same environment.

The objective of this project is to simulate and evaluate reinforcement learning algorithms that enable autonomous vehicles to perform complex driving tasks,
such as merging, lane changing, and overtaking, while ensuring safety and optimizing traffic flow.

Specifically, the project will focus on \textbf{simulating scenarios at road intersections where multiple autonomous vehicles must determine the order of crossing
and appropriate speeds, aiming to maximize traffic efficiency and minimize collision risks.}

This will be achieved using an agent-based simulation framework - \textbf{\textit{Highway Env}}\cite{highwayenv} - where a group of four agents, each trained with different Deep Reinforcement Learning (DRL) policies, will face dynamic environmental changes. The agents will
be tested under various combinations of environmental variables (e.g., traffic density,vehicle speed) to evaluate their behavior and decision-making processes in real-time. 

This experimental setup will create a Multi-Agent System (MAS) within a dynamic environment, concentrating on decision-making strategies for autonomous driving.

Through this project, we aim to address critical questions regarding the scalability and robustness of DRL models in autonomous driving. 

In particular, the research will explore how well these algorithms generalize to unseen environments — a key challenge for deep learning-based approaches. 

The insights gained can inform the real-world applicability of DRL for autonomous vehicles, especially in unpredictable or changing environments.
